Peer-to-Peer 6502 Cellular Automata

### 2018-07-03 paper.tex
tidying

\section{Cellular automata}

@@

Each cell has 256 bytes (one ``page'') of state.
All cells' bytes are initially zero, unless otherwise specified
(including, implicitly, cells whose coordinates are outside the CA).
These bytes are the ``storage'' of the virtual machine.

@@

\section{Blankets}
\label{sec:Blankets}

@@

We refer to these cells as the {\bf blanket} of the CA.
Previously, we specified that their state was implicitly initialized to zero.
More generally, we may refer to the initial (and perpetual, throughout the execution of an update)
state of these cells as the CA's {\bf blanket state}.
This blanket state is zero until otherwise specified, but may be affected
by interactions with neighboring CAs in the infinite vector space,
as for example by the blockchain of Section~\ref{sec:Blockchain}.

@@

The CA has an associated blockchain, defined as in \cite{Nakamoto2008}.
The proof-of-work is adjusted to include updating the CA,
and the mining incentive is adjusted to include redemption of coins minted by adjacent CAs
(this also updates the blanket cells accounted for by those CAs).

Specifically, let the proof-of-work include $C \times Z$ updates of the CA,
where $Z$ is the number of zeroes required by the network at the start of the hash function for a valid block,
and $C$ is the number of cycles expected in the blockchain update time
(which for bitcoin is 10 minutes).

Let the definition of a block include the coordinates $(\alpha_x,\alpha_y,\alpha_z,L)$;
these coordinates, together with the number of updates,
must be used to seed the random number generator for the $Z$ updates,
and the block must include the $256 L^3$ bytes describing the state of the CA following the update.

@@

>>>>

\section{Cellular Automaton}

\subsection{Storage}
\label{sec:Storage}

@@

Each cell has 256 bytes (one page) of state.
All cells' bytes are initially zero, unless otherwise specified
(including, implicitly, cells whose coordinates are outside the CA; see also Section~\ref{sec:Blankets}).
These bytes are the storage of the virtual machine.

\subsection{Virtual machine}

@@

\subsection{Blankets}
\label{sec:Blankets}

@@

We refer to these cells as the {\bf blanket} of the CA.
Earlier, in Section~\ref{sec:Storage}, we specified that the state of these cells was implicitly initialized to zero.
More generally, we may refer to the initial (and perpetual, throughout the execution of an update)
state of these cells as the CA's {\bf blanket state}.
This blanket state is zero until otherwise specified, but may be affected
by interactions with neighboring CAs in the infinite vector space,
as for example by the blockchain of Section~\ref{sec:Blockchain}.

@@

The CA has an associated blockchain, defined as in \cite{Nakamoto2008}.
Updates are incentivized by mining,
and the reward for mining is adjusted to include redemption of coins mined by adjacent CA blockchains
(this also updates the blanket cells accounted for by those CAs).

\subsection{Updates}

A valid block must include the $256 \times L^3$ bytes describing the state of the CA following $C$ updates
from the state at the end of the previous block.
$C$ is the number of cycles per cell expected in the blockchain update time
(which for bitcoin is 10 minutes).

Let the definition of a block include the coordinates $(\alpha_x,\alpha_y,\alpha_z,L)$;
these coordinates, together with the number of updates,
must be used to seed the random number generator for the $Z$ updates.

\subsection{Writes}

@@

\subsection{Adjacencies}
